Paper # 1 - Figures

### 2020-03-19 papers/paper-1/paper_1_figures.Rmd
remaking paper 1 figures

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(sf)
library(rworldmap)
library(rmapshaper)
library(tidyverse)

@@

```{r}
# Plot themes and shapefiles
map_theme <- theme(panel.background = element_rect(fill ="black"),
        plot.background = element_rect(fill = "black"),
        legend.background=element_rect(fill="black"),
        legend.text = element_text(color = "white", size = 16),
        legend.title = element_text(color = "white", size = 16),
        legend.title.align = 1,
        legend.direction="horizontal",
        legend.position = "bottom",
        legend.justification = "center",
        axis.text = element_text(color = "white", size = rel(1)),
        panel.grid.major = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

plot_theme <- theme_bw()

# Land shapefile
world_land <- st_as_sf(rworldmap::countriesLow) ## data(countriesLow) is from the rworldmap package

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = (A_subs+B_subs+C_subs)/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag")
```

@@

Now let's calculate and plot the median bad subsidy intensities by lat/lon bin and FAO region.

```{r}
median_breaks <- seq(0,6, by = 1)
median_limits <- c(0,6)
median_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

median_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_B_grid_map

@@

@@

```{r}
region_median_breaks <- seq(0,2, by = 0.5)
region_median_limits <- c(0,2)
region_median_labels <- c("0", "0.5", "1", "1.5", paste0("\u2265","2"))

median_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_B_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_B_region_map

@@

@@

Do means too.

```{r}
mean_breaks <- seq(0,6, by = 1)
mean_limits <- c(0,6)
mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity ($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

Let's make ones for the weighted means too using fishing KWh as the weights.

```{r}
weighted_mean_breaks <- seq(0,6, by = 1)
weighted_mean_limits <- c(0,6)
weighted_mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

weighted_mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
region_weighted_mean_breaks <- seq(0,4, by = 1)
region_weighted_mean_limits <- c(0,4)
region_weighted_mean_labels <- c("0", "1", "2", "3", paste0("\u2265","4"))

weighted_mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_weighted_mean_limits, 
                       breaks = region_weighted_mean_breaks,
                       labels = region_weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

### Stock status

@@

upsides_regional_averages <- upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(mean_f_v_fmsy = mean(fv_fmsy),
            mean_weighted_f_v_fmsy = weighted.mean(fv_fmsy, w = msy),
            median_f_v_fmsy = median(fv_fmsy),
            mean_b_v_bmsy = mean(bv_bmsy),
            mean_weighted_b_v_bmsy = weighted.mean(bv_bmsy, w = msy),
            median_b_v_bmsy = median(bv_bmsy))

@@

```{r}

upsides_regional_averages_spatial <- fao_regions %>%
  right_join(upsides_regional_averages, by = c("fao_region" = "region_fao_split"))

>>>>

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(sf)
library(rworldmap)
library(rmapshaper)
library(RColorBrewer)
library(cowplot)
library(tidyverse)

source(here::here("functions", "MapMaker.R"))

@@

```{r}
# Land shapefile
world_land <- st_as_sf(rworldmap::countriesLow) ## data(countriesLow) is from the rworldmap package

@@

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C) %>%
  mutate(BC_subs = B_subs + C_subs,
         tot_subs = A_subs + B_subs + C_subs)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         BC_subs_KWh = BC_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = tot_subs/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag") %>%
  mutate(B_subs = B_subs_KWh*fishing_KWh_lat_lon,
         BC_subs = BC_subs_KWh*fishing_KWh_lat_lon,
         C_subs = C_subs_KWh*fishing_KWh_lat_lon,
         tot_subs = tot_subs_KWh*fishing_KWh_lat_lon)

# Summarize by lat/lon
subsidy_intensity_binned <- effort_binned_sub_intensity %>%
  group_by(lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            B_subs = sum(B_subs, na.rm = T),
            BC_subs = sum(BC_subs, na.rm = T),
            C_subs = sum(C_subs, na.rm = T),
            tot_subs = sum(tot_subs, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))

# Summarize by fao region
subsidy_intensity_region <- effort_binned_sub_intensity %>%
  group_by(fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
            B_subs = sum(B_subs, na.rm = T),
            BC_subs = sum(BC_subs, na.rm = T),
            C_subs = sum(C_subs, na.rm = T),
            tot_subs = sum(tot_subs, na.rm = T),
            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
```

@@

## Total Subsidies

### Subsidy Intensities by Lat/Lon

```{r}
# Median
median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_tot_grid_legend <- get_legend(w_mean_subsidy_intensity_tot_grid_map)

subsidy_intensity_tot_grid_map <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                            intensity_tot_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_tot_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)

### Subsidy Intensities by Region

```{r}
# Median
median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_tot_region_legend <- get_legend(w_mean_subsidy_intensity_tot_region_map)

subsidy_intensity_tot_region_map <- plot_grid(median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                            intensity_tot_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_tot_region_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)

## Bad Subsidies

### Subsidy Intensities by Lat/Lon

```{r}
# Median
median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_B_grid_legend <- get_legend(w_mean_subsidy_intensity_B_grid_map)

subsidy_intensity_B_grid_map <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                            intensity_B_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_B_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

### Subsidy Intensities by Region

```{r}
# Median
median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_B_region_legend <- get_legend(w_mean_subsidy_intensity_B_region_map)

subsidy_intensity_B_region_map <- plot_grid(median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                            intensity_B_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_B_region_map
ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

## Bad + Ambiguous Subsidies

### Subsidy Intensities by Lat/Lon

```{r}
# Median
median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_BC_grid_legend <- get_legend(w_mean_subsidy_intensity_BC_grid_map)

subsidy_intensity_BC_grid_map <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                            intensity_BC_grid_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_BC_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)

### Subsidy Intensities by Region

```{r}
# Median
median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
intensity_BC_region_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)

subsidy_intensity_BC_region_map <- plot_grid(median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                            intensity_BC_region_legend,
                                            ncol = 1,
                                            rel_heights = c(1,1,1,0.2),
                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                            label_x = c(-0.04,-0.03,-0.1,0),
                                            align = "v")

subsidy_intensity_BC_region_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)

## Stock status

@@

upsides_region <- upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(mean_f_v_fmsy = mean(fv_fmsy, na.rm = T),
            w_mean_f_v_fmsy = weighted.mean(fv_fmsy, w = msy, na.rm = T),
            med_f_v_fmsy = median(fv_fmsy, na.rm = T),
            mean_b_v_bmsy = mean(bv_bmsy, na.rm = T),
            w_mean_b_v_bmsy = weighted.mean(bv_bmsy, w = msy, na.rm = T),
            med_b_v_bmsy = median(bv_bmsy, na.rm = T),
            tot_msy = sum(msy, na.rm = T)) %>%
  rename(fao_region = region_fao_split)

@@

### F/Fmsy by Region

```{r}
# Median
median_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "med_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

ggsave(paste0(results_dir, "median_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "mean_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
